Accuracy and precision of zero-heat-flux temperature monitoring: a systematic review and meta- analysis

### 2019-10-01 manuscript/manuscript.Rmd
minor

```{r echo=FALSE, include=FALSE}
library(tidyverse)
library(kableExtra)
library(purrr)
library(ggplot2)
library(dplyr)
library(qwraps2)
library(knitr)
```

@@

```{r load-data, include=FALSE}
data <- readxl::read_xlsx(here::here("data", "zhf_extracted.xlsx"))
```

```{r meta-analysis-prep, include=FALSE}
data <- data %>%

  mutate(c = N/n)

@@

data <-  if (data$corrected == "Yes"){

  mutate(data, s2 = ((upper - bias)/1.96)^2)

  } else {

    mutate(data, s2 = ((upper - bias)/1.96)^2)*((N-1)/(N-c))

    }

@@

data_core_op <- data%>% #eshragi intraop
    filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
  filter (clinical_setting=="Intraoperative")

@@

```{r format-result-function, include=FALSE}
format_results <- function(group){
out <- loa_maker(group$bias,group$V_bias, group$logs2, group$V_logs2)
out <- round(out, digits=1)
out <- out %>% 
  mutate(Participants = sum(group$n_count, na.rm=T)) %>% 
  mutate(Measurements = format(sum(group$N, na.rm = T), big.mark=",", scientific = FALSE)) %>% 
  mutate(Studies = length(unique(group$Study))) %>% 
  select(Studies, m, Participants, Measurements, bias_mean, sd2_est, tau_est, LOA_L, LOA_U, CI_L_rve, CI_U_rve) %>% 
  rename("Comparisons" = m)
out

@@

    g <- g + stat_function(fun=dnorm, args = list(pooled_bias, pooled_sd), colour ="lightcoral", alpha = 0.05) + 
      stat_function(fun=dnorm, args = list(pooled_bias, pooled_sd), colour = NA, geom="area", fill="lightcoral", alpha = 0.6) + 
      scale_x_continuous(limits = c(-3.5,3.5)) + labs(x = expression('Difference between core and ZHF temperature measurements in'*~degree*C*''))+
      scale_y_continuous(name = "Density \n", limits = c(0,2.5)) +  
      #labs(title = "\nOuter confidence intervals for pooled limits of agreement\n\n  Pooled limits of agreement")+
      theme(plot.title = element_text(hjust = 0.5, margin = margin(t=10, b=-32), size=10),
            axis.text=element_text(hjust = 0.5, size=10),                                                                        
            axis.title=element_text(hjust = 0.5, size=10),
            axis.line=element_line(colour="black", size=0.2),
            panel.background = element_blank(),
            axis.ticks = element_blank(), 
            plot.caption = element_text(hjust = 0)) #+ 
      #CI lines that extend to arrow tips
      # geom_segment(aes(x=LOA_u, y=0, xend=LOA_u, yend=2.25), size = 0.3, linetype="dashed")+ 
      # geom_segment(aes(x=LOA_l, y=0, xend=LOA_l, yend=2.25), size = 0.3, linetype="dashed")+
      # geom_segment(aes(x=LOA_u_CI, y=0, xend=LOA_u_CI, yend=2.48), size = 0.3)+
      # geom_segment(aes(x=LOA_l_CI, y=0, xend=LOA_l_CI, yend=2.48), size = 0.3)#+
      # 
      # geom_segment(aes(x=0, y=2.48, xend=LOA_u_CI, yend=2.48), size = 0.4, arrow = arrow(length = unit(0.03, "npc")))+ #R arrow high
      # geom_segment(aes(x=0, y=2.48, xend=LOA_l_CI, yend=2.48), size = 0.4, arrow = arrow(length = unit(0.03, "npc")))+ #L arrow high
      # geom_segment(aes(x=0, y=2.25, xend=LOA_u, yend=2.25), size = 0.4,  arrow = arrow(length = unit(0.03, "npc")))+ #R arrow low
      # geom_segment(aes(x=0, y=2.25, xend=LOA_l, yend=2.25), size = 0.4,  arrow = arrow(length = unit(0.03, "npc"))) #L arrow low
g
```

@@

>>>>

```{r echo=FALSE, include=FALSE}
library(tidyverse)
library(kableExtra)
library(qwraps2)
library(knitr)
```

@@

```{r load-data, include=FALSE}
data <- readxl::read_xlsx(here::here("app", "data", "zhf_extracted.xlsx"))
```

```{r meta-analysis-prep, include=FALSE}
data <- data %>%
  mutate(c = N/n)

@@

data <- data %>% 
  mutate(s2 = case_when(corrected == "Yes"  ~ ((upper - bias)/1.96)^2,
         corrected == "No" ~  ((upper - bias)/1.96)^2*(N-1)/(N-c)
                        )
        )

@@

data_core_op <- data %>% #eshragi intraop
    filter(comparison=="PA"|comparison=="Bladder"|comparison=="Eso" | comparison =="Rectal"|comparison =="Ax"|comparison =="Iliac") %>%
  filter (clinical_setting=="Intraoperative")

@@

```{r format-result-function, include=FALSE}
format_results <- function(group){
out <- loa_maker(group$bias,group$V_bias, group$logs2, group$V_logs2)
out <- round(out, digits=2)
out <- out %>% 
  mutate(Participants = sum(group$n_count, na.rm=T)) %>% 
  mutate(Measurements = format(sum(group$N, na.rm = T), big.mark=",", scientific = FALSE)) %>% 
  mutate(Studies = length(unique(group$Study))) %>% 
  select(Studies, m, Participants, Measurements, bias_mean, sd2_est, tau_est, LOA_L, LOA_U, CI_L_rve, CI_U_rve) %>% 
  rename("Comparisons" = m)
out

@@

    g <- g + stat_function(fun=dnorm, args = list(pooled_bias, pooled_sd), colour ="lightcoral", alpha = 0.05) + 
      stat_function(fun=dnorm, args = list(pooled_bias, pooled_sd), colour = NA, geom="area", fill="lightcoral", alpha = 0.6) + 
      scale_x_continuous(limits = c(-3.5,3.5), breaks = c(-2, -1, 0, 1, 2)) + labs(x = expression('Difference between core and ZHF temperature measurements in'*~degree*C*''))+
      scale_y_continuous(name = "Density \n", limits = c(0,2.5)) +  
      #labs(title = "\nOuter confidence intervals for pooled limits of agreement\n\n  Pooled limits of agreement")+
      theme(plot.title = element_text(hjust = 0.5, margin = margin(t=10, b=-32), size=10),
            axis.text=element_text(hjust = 0.5, size=10),                                                                        
            axis.title=element_text(hjust = 0.5, size=10),
            axis.line=element_line(colour="black", size=0.2),
            panel.background = element_blank(),
            axis.ticks = element_blank(), 
            plot.caption = element_text(hjust = 0)) #+ 
      #CI lines that extend to arrow tips
      # geom_segment(aes(x=LOA_u, y=0, xend=LOA_u, yend=2.25), size = 0.3, linetype="dashed")+ 
      # geom_segment(aes(x=LOA_l, y=0, xend=LOA_l, yend=2.25), size = 0.3, linetype="dashed")+
      # geom_segment(aes(x=LOA_u_CI, y=0, xend=LOA_u_CI, yend=2.48), size = 0.3)+
      # geom_segment(aes(x=LOA_l_CI, y=0, xend=LOA_l_CI, yend=2.48), size = 0.3)#+
      # 
      # geom_segment(aes(x=0, y=2.48, xend=LOA_u_CI, yend=2.48), size = 0.4, arrow = arrow(length = unit(0.03, "npc")))+ #R arrow high
      # geom_segment(aes(x=0, y=2.48, xend=LOA_l_CI, yend=2.48), size = 0.4, arrow = arrow(length = unit(0.03, "npc")))+ #L arrow high
      # geom_segment(aes(x=0, y=2.25, xend=LOA_u, yend=2.25), size = 0.4,  arrow = arrow(length = unit(0.03, "npc")))+ #R arrow low
      # geom_segment(aes(x=0, y=2.25, xend=LOA_l, yend=2.25), size = 0.4,  arrow = arrow(length = unit(0.03, "npc"))) #L arrow low
g
```

@@

We did not include studies that used the Temple Touch Pro. This is a thermometer similar to the zero-heat-flux device in that it is placed cutaneously, but the underlying technology is different. There have been x studies that evaluated the Temple Touch Pro device with promising results.
